manuscript - APP

### 2018-09-25 R/manuscript_app.Rmd
fig 3 in function

```{r Figure 3a}
df_exp1b %>% 
  ggplot(aes(x = targetk, y = accuracy) + 
    facet_grid(~restk, 
               labeller = labeller(
        xfacet = c(`2` = expression("Target's"~kappa~"=2"), 
                   `4` = expression("Target's"~kappa~"=4"),
                   `8` = expression("Target's"~kappa~"=8"),
                   `16` = expression("Target's"~kappa~"=16"),
                   `64` = expression("Target's"~kappa~"=64"))

    )) +
    stat_summary(fun.data = "mean_cl_boot") + 
    stat_summary(fun.y = mean, geom = "line") + 
    geom_hline(yintercept=0.125) + 
    theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
    ylab("Accuracy") + 
    ylim(0,1)+
    scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,2,4,8,16,32,64,128),labels = c("1","2","4","8","16","32","64","128"), trans = "log2") + 
    geom_vline(xintercept = restk_var, linetype = 2) +
    ggtitle(ggtit) +
    theme(plot.title = element_text(hjust = 0.5))
```

>>>>

```{r Figure 3a}

p <- plot_fig3b()  
p

ggsave(file.path(plot_pth, "Figure3b.png"), p, width = 12, height = 6)
